A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-17 paper/paper.Rnw
Fixing references

\fix{Figures \ref{fig:single-exemplars} and \ref{multi-exemplars} provide representative examples of classifications across multiple categories; it is also useful to examine many cases within a given shape.} \autoref{fig:chevrons-consistency} shows a number of images containing chevrons. The top four rows show regularly repeating chevron patterns and seems to indicate that the model optimally identifies chevrons of a certain width; wide chevrons cross into the realm of bowties, whereas narrow chevrons become indistinguishable from lines. The next six rows show individual and closed chevrons. There is a significant amount of confusion between these wider chevrons and quadrilaterals. Finally, the bottom four rows show less-than-standard chevrons. The rounded chevron has a much lower prediction than those with sharper angles, but still exceeds the EER for chevron; the white chevrons are confounded with overlaid circles, which introduces a complexity that the model attributes to text.

@@

\mt{\paragraph{Accuracy by class}}
\fix{Figures \ref{fig:single-exemplars}-\ref{fig:circle-text-consistency} show predictions for a number of individual images. Many of the misclassifications in these examples are not just seen in individual images, but rather exist systematically in a class.} A confusion matrix is a type of visualization that summarizes the relationships between the labels assigned to an image and the labels predicted by the model across all test data, and is a helpful diagnostic tool to understand which classes are systematically misclassified.} \mt{The confusion matrix for \fix{our model} is presented in \autoref{fig:confusion_matrix}}. The values along the diagonal represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, since a single image may truly contain multiple shapes, the values have been adjusted to remove the effect of any true positives from the calculation of false positive proportions.
%\svp{As a result of this adjustment, the probabilities off-diagonal are the proportion ... need to explain the conditional probability we're showing here}
\fix{As a result of this adjustment, the off-diagonal values are the proportion of images within a true class that are falsely labeled as containing another class that has not been identified in the image. }%\svp{I can't remember exactly how we're doing that, but we may want to look more closely at that - if we set everything to NA instead of 0, the rate calculations would be higher than expected}
For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any image that truly contains both triangles and quadrilaterals is removed before calculating the proportion of false quadrilateral labels. \mt{Note that this matrix is not symmetric---the proportion of images containing text that are falsely predicted to contain circles is not necessarily equal to the proportion of images containing circles that are falsely predicted to contain text.}

@@

<<brands-within-shapes>>=
shapes <- lapply(X = classes, function(x){
  out <- df_shoes[df_shoes[,x, drop = T],]
  out$shape <- x
  out
})
names(shapes) <- classes

>>>>

\fix{Figures \ref{fig:single-exemplars} and \ref{fig:multi-exemplars} provide representative examples of classifications across multiple categories; it is also useful to examine many cases within a given shape.} \autoref{fig:chevrons-consistency} shows a number of images containing chevrons. The top four rows show regularly repeating chevron patterns and seems to indicate that the model optimally identifies chevrons of a certain width; wide chevrons cross into the realm of bowties, whereas narrow chevrons become indistinguishable from lines. The next six rows show individual and closed chevrons. There is a significant amount of confusion between these wider chevrons and quadrilaterals. Finally, the bottom four rows show less-than-standard chevrons. The rounded chevron has a much lower prediction than those with sharper angles, but still exceeds the EER for chevron; the white chevrons are confounded with overlaid circles, which introduces a complexity that the model attributes to text.

@@

\mt{\paragraph{Accuracy by class}}
\fix{Figures \ref{fig:single-exemplars}-\ref{fig:circle-text-consistency} show predictions for a number of individual images. Many of the misclassifications in these examples are not just seen in individual images, but rather exist systematically in a class.} A confusion matrix is a type of visualization that summarizes the relationships between the labels assigned to an image and the labels predicted by the model across all test data, and is a helpful diagnostic tool to understand which classes are systematically misclassified. \mt{The confusion matrix for \fix{our model} is presented in \autoref{fig:confusion_matrix}}. The values along the diagonal represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, since a single image may truly contain multiple shapes, the values have been adjusted to remove the effect of any true positives from the calculation of false positive proportions.
%\svp{As a result of this adjustment, the probabilities off-diagonal are the proportion ... need to explain the conditional probability we're showing here}
\fix{As a result of this adjustment, the off-diagonal values are the proportion of images within a true class that are falsely labeled as containing another class that has not been identified in the image. }%\svp{I can't remember exactly how we're doing that, but we may want to look more closely at that - if we set everything to NA instead of 0, the rate calculations would be higher than expected}
For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any image that truly contains both triangles and quadrilaterals is removed before calculating the proportion of false quadrilateral labels. \mt{Note that this matrix is not symmetric---the proportion of images containing text that are falsely predicted to contain circles is not necessarily equal to the proportion of images containing circles that are falsely predicted to contain text.}

@@

<<brands-within-shapes, fig.cap = "Caption here">>=
shapes <- lapply(X = classes, function(x){
  out <- df_shoes[df_shoes[,x, drop = T],]
  out$shape <- x
  out
})
names(shapes) <- classes
